---
title: "COMP1014_Assigment 1"
author: "Prema Santhi"
date: "2024-11-29"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Calling data
```{r}
dataset=read.csv("AssessmentSet1.csv")
```

# Question 1
Test whether there is an association between shopping frequency and gender.

Make sure you:

a. Visualize the data,

b. Show all the key steps of hypothesis testing,

c. Interpret the results, both statistically and in the context of the case. In no more than 3 sentences explain what the results reveal about how store location is associated with gender, and how might these insights inform marketing strategies or store management decisions?

## Hypothesis
H0 = Rows and columns are independent.  In other word,

H0: There is no relation between shopping frequency and gender.


Ha = rows and columns are not independent. In other word,

Ha: There is a relation between shopping frequency and gender.

## Approach
The shopping frequency and gender were grouped together using table.
```{r}
shoppingGender.data= table(dataset$Gender,dataset$ShoppingFrequency)
shoppingGender.data
```

## Plotting the data
Visualize the data using barplot.

```{r}
barplot(shoppingGender.data, beside=TRUE, col=c("light green", "light blue","red"),
        legend=c("Female", "Male","Other"),
        main="Association between shopping frequency and gender")
```

## Testing
Before we conduct a testing using chi-square, we need to determine the expected number.
```{r}
test=chisq.test(shoppingGender.data)
test$expected
```

As seen in the output, there is one value with expected count less than 5. So the simulation is required.
```{r}
chisq.test(shoppingGender.data, simulate.p.value = TRUE, B=1000)
```

After conducting the simulation, we got 0.965 for the p value.

## Conclusion
The p-value is greater than 0.05, therefore we cannot reject the null hypothesis and say that there is no relation between shopping frequency and gender.

According to the result, all gender tend to have the same shopping frequency. It means that the store need to look after the products that each gender are more frequently buy at a specific time (daily, monthly, etc.).

# Question 2
Test whether the mean age of customers who shop at Hornsby is significantly greater than
that of customers who shop at Bondi.

Make sure you:

a. Visualize the data,

b. Show all the key steps of hypothesis testing,

c. Interpret the results, both statistically and in the context of the case. In no more than three sentences, explain what the results reveal about the shopping behaviour, and how these findings could be relevant for marketing or product placement strategies.


## Hypothesis
H0 = miu1 = miu2.  In other word,

H0: There is no difference in mean age of customers who shop at Hornsby and the customers who shop at Bondi.


Ha = miu1 > miu2. In other word,

Ha: The mean age of customers who shop at Hornsby is significantly greater than
the customers who shop at Bondi.

## Approach
Divide the age and store location at Hornsby using subset.
```{r}
age.horn=subset(dataset, StoreLocation=="Hornsby", Age, drop=TRUE)
age.horn
```

Divide the age and store location at Bondi using subset.
```{r}
age.bon=subset(dataset, StoreLocation=="Bondi", Age, drop=TRUE)
age.bon
```

## Plotting the data

First, we visualize the data of customer who went shopping at Hornsby.
```{r}
hist(age.horn,xlab="Age",main = "Customer at Hornsby", col="light blue")
```

Second, we visualize the data of customer who went shopping at Bondi.
```{r}
hist(age.bon,xlab="Age",main = "Customer at Bondi",col="light green")
```


## Testing the data
Test the means using t-test.
```{r}
t.test(age.horn,age.bon,alternative="greater",var.equal = TRUE)
```

The p-value is 0.4863.

## Conclusion
Based on the p-value, we cannot reject the null hypothesis. So we say that there is no difference in mean age of customers who shop at Hornsby and the customers who shop at Bondi. By means that the manager need to sell the products that are usually bought by different stage of age (referring to the data: from teenager to elderly).

# Question 3
Test whether there is a significant difference in the mean satisfaction score across different genders.

Make sure you:

a. Visualize the data,

b. Show all the key steps of hypothesis testing,

c. Interpret the results, both statistically and in the context of the case. In no more than three sentences, explain what the results reveal about the difference mean satisfaction score across different genders.

d. Additionally, identify which specific genders show significant differences and explain how these insights could be used to make informed business decisions (only print the significant results).

## Hypothesis
H0 = miu1 = miu2.  In other word,

H0: There is no significant difference in the mean satisfaction score across different genders.


Ha = miu1 != miu2. In other word,

Ha: There is a significant difference in the mean satisfaction score across different genders

## Approach
Divide the gender and satisfaction score using table
```{r}
satisfac=table(dataset$Gender, dataset$SatisfactionScore)
satisfac
```

The row names represent satisfaction score in a range between 3-10.

## Plotting the data
```{r}
barplot(satisfac, beside=TRUE,
        legend=c("Female","Male","Other"))
```

## Testing
Next, using table to know whether the sample size is large enough or not for each category.
```{r}
table(dataset$Gender)
```

All the sample size are greater than 30. So we can directly use the oneway test
```{r}
oneway.test(SatisfactionScore~Gender, data=dataset, var.equal = TRUE)
```

After the testing, the p-value is 0.00. Since the p-value is smaller than 0.05, we can reject the null hypothesis and state that there is a difference between satisfaction score and the gender. 

## Which one is different?
To know which one is different, we can test using post-hoc comparison.
```{r}
diff.aov=aov(SatisfactionScore~Gender,data=dataset)
TukeyHSD(diff.aov)
```

Based on the p.value, male and female shows significant different in giving satisfaction score.

## Conclusion
Because men and women shows differences in giving satisfaction score, the owner need to  analyze what happened in their store.There might be cases where they ignore the female customer or they have some problem between serving different gender. This data might help the owner to make decision regarding the action they need to take as soon as possible.

# Question 4

Test if age can be used to predict purchase amount. Assess the strength of the predictive
power of age for purchase amount.

Make sure you:

a. Visualize the data,

b. Show all the key steps of hypothesis testing,

c. Interpret the results, both statistically and in the context of the case. In no more than three sentences, explain what the results reveal about the relationship
between age and purchase amount.

d. Additionally, use your model to predict the purchase amount for a customer who is 33 years old. Comment on the appropriateness of this prediction and justify your answer.

e. Examine the residuals of your regression model: What do they indicate about the model's performance and any potential issues with the assumptions of your model?

## Hypothesis
H0 = Beta1 = 0. In other word,

Ho: Age does not affect or predict the purchase amount 


Ha = Beta1 !=0. In other word,

Ha: Age does affect or predict the purchase amount


## Approach
Using permutation approach,
```{r}
slope.perm=replicate(1000,{
  age.perm=sample(dataset$Age)
  perm=lm(PurchaseAmount~age.perm,data=dataset)
  coef(perm)[2]
})
```

Now compute the slope of the data
```{r}
act.predict=lm(PurchaseAmount~Age,data=dataset)
slope=coef(act.predict)[2]
mean(slope.perm>abs(slope))+mean(slope.perm<-abs(slope))
```

The p-value is large, so we can reject the null hypothesis and say that the slope of the linear regresion is not 0. It means that age does have significant impact on the purchase amount.

## Testing
```{r}
act.predict=lm(PurchaseAmount~Age,data=dataset)
summary(act.predict)
```

The Residuals are quite large (70.46), so it difference between the observed data and the prediction is large. Then the transformation is required.

### Transformation
Using log transformation:
```{r}
trans=lm(log(PurchaseAmount)~Age,data=dataset)
summary(trans)
```

After the transformation the Residuals become smaller. Then we can conclude the prediction using this equation.

## Equation
y = a+bx

Purchase amount = a+b*Age

Based on the result,

The equation is: Purchases amount = 4.179577 + (0.012821*Age)

## Plotting the data
Plot the transformed function.
```{r}
plot(trans)
```

The data are quite close to 0.

## Predict y using the model
Predict the purchase amount for a customer who is 33 years old.
```{r}
new.data=predict(trans,newdata =data.frame(Age=33))
exp(new.data) # because it is in the form of logarithm (log(y)), so we need to find the y
```

Because the Residuals are small, then the prediction might be accurate. So when the customer is 33 years old, the total cost they pay is 99.7.