---
title: "COMP1014_Assigment 1"
author: "Prema Santhi"
date: "2024-11-29"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Calling data
```{r}
dataset=read.csv("AssessmentSet1.csv")
```

# Question 1
Test whether there is an association between shopping frequency and gender.

Make sure you:

a. Visualize the data,

b. Show all the key steps of hypothesis testing,

c. Interpret the results, both statistically and in the context of the case. In no more than 3 sentences explain what the results reveal about how store location is associated with gender, and how might these insights inform marketing strategies or store management decisions?

## Hypothesis
H0 = Rows and columns are independent.  In other word,

H0: There is no relation between shopping frequency and gender.


Ha = rows and columns are not independent. In other word,

Ha: There is a relation between shopping frequency and gender.

## Approach
The shopping frequency and gender were grouped together using table.
```{r}
shoppingGender.data= table(dataset$Gender,dataset$ShoppingFrequency)
shoppingGender.data
```

## Plotting the data
Visualize the data using barplot.

```{r}
barplot(shoppingGender.data, beside=TRUE, col=c("light green", "light blue","red"),
        legend=c("Female", "Male","Other"),
        main="Association between shopping frequency and gender")
```

## Testing
Before we conduct a testing using chi-square, we need to determine the expected number.
```{r}
test=chisq.test(shoppingGender.data)
test$expected
```

As seen in the output, there is one value with expected count less than 5. So the simulation is required.
```{r}
chisq.test(shoppingGender.data, simulate.p.value = TRUE, B=1000)
```

After conducting the simulation, we got 0.965 for the p value.

## Conclusion
The p-value is greater than 0.05, therefore we cannot reject the null hypothesis and say that there is no relation between shopping frequency and gender.

According to the result, all gender tend to have the same shopping frequency. It means that the store need to look after the products that each gender are more frequently buy at a specific time (daily, monthly, etc.).

# Question 2
Test whether the mean age of customers who shop at Hornsby is significantly greater than
that of customers who shop at Bondi.

Make sure you:

a. Visualize the data,

b. Show all the key steps of hypothesis testing,

c. Interpret the results, both statistically and in the context of the case. In no more than three sentences, explain what the results reveal about the shopping behaviour, and how these findings could be relevant for marketing or product placement strategies.


## Hypothesis
H0 = miu1 = miu2.  In other word,

H0: There is no difference in mean age of customers who shop at Hornsby and the customers who shop at Bondi.


Ha = miu1 > miu2. In other word,

Ha: The mean age of customers who shop at Hornsby is significantly greater than
the customers who shop at Bondi.

## Approach
Divide the age and store location at Hornsby using subset.
```{r}
age.horn=subset(dataset, StoreLocation=="Hornsby", Age, drop=TRUE)
age.horn
```

Divide the age and store location at Bondi using subset.
```{r}
age.bon=subset(dataset, StoreLocation=="Bondi", Age, drop=TRUE)
age.bon
```

## Plotting the data

First, we visualize the data of customer who went shopping at Hornsby.
```{r}
hist(age.horn,xlab="Age",main = "Customer at Hornsby", col="light blue")
```

Second, we visualize the data of customer who went shopping at Bondi.
```{r}
hist(age.bon,xlab="Age",main = "Customer at Bondi",col="light green")
```


## Testing the data
Test the means using t-test.
```{r}
t.test(age.horn,age.bon,alternative="greater",var.equal = TRUE)
```

The p-value is 0.4863.

## Conclusion
Based on the p-value, we cannot reject the null hypothesis. So we say that there is no difference in mean age of customers who shop at Hornsby and the customers who shop at Bondi. By means that the manager need to sell the products that are usually bought by different stage of age (referring to the data: from teenager to elderly).